---
title: "TEST"
author: "Liuxuan (Kelly) Yu and Lindsay Tober"
date: "August 8, 2016"
output: html_document
fig_caption: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# STA 380 Homework 1


## Market segmentation

A market-research study was completed based on tweets of followers of  NutrientH20 Twitter account, where they had an advertising firm analyze tweets of its followers over a seven day period in June 2014 so as to to explain its social-media audence in order to better hone its audience.  Initial categorization was completed on the tweets to assign them different labels.  For example, a hypothetical post such as "I'm really excited to see grandpa go wreck shop in his geriatic soccer league this Sunday!" might be categorized as both "family" and "sports."

```{r include=FALSE}
# Setup
library(wordcloud)
library(textir)
library(flexclust)
library(pander)
library(mosaic)

# Market-research study using followers of Consumer Brand Twitter account
marketsegmentation <- read.csv("social_marketing.csv", row.names=1)
head(marketsegmentation)
summary(marketsegmentation)

# Scaling the data
marketsegmentation_scaled <- scale(marketsegmentation, center=TRUE, scale=TRUE) 

# K-means clustering
marketsegmentation_cluster <- kmeans(marketsegmentation_scaled, centers = 5)
marketsegmentation_cluster$centers
marketsegmentation_cluster$cluster

# Plot K-means
plot(marketsegmentation_scaled[,"family"], marketsegmentation_scaled[,"shopping"],
    type="n", xlab="Family", ylab="Shopping")
text(marketsegmentation_scaled[,"family"], marketsegmentation_scaled[,"shopping"], #
    labels=rownames(marketsegmentation), 
    col=rainbow(3)[marketsegmentation_cluster$cluster]) 


# All centroids
#important_terms<-print(apply(kmeans_marketsegmentation$centers,1,function(x) colnames(Z)[order(x, decreasing=TRUE)[1:10]]))

## K-means++
# Scaled per-document phrase frequencies
marketsegmentation_freq = marketsegmentation/rowSums(marketsegmentation)
Z = scale(marketsegmentation_freq)

# Run K-means
kmeans_marketsegmentation <- kmeans(Z, 5)  


# All centroids
#important_terms<-print(apply(kmeans_marketsegmentation$centers,1,function(x) colnames(Z)[order(x, decreasing=TRUE)[1:10]]))

# A word cloud
#wordcloud(colnames(Z), kmeans_marketsegmentation$centers[2,], min.freq=0, max.words=100)

```

Using K-means clustering, we segmented NutrientH20's Twitter followers into 5 clusters and gathered the top categories for each cluster:

<center>
**Table 2:** Top 10 categories by cluster of twitter followers for NutrientH20.
</center>
</br>

      1                 2                 3                 4               5                 
 [1,] "dating"          "online_gaming"   "tv_film"         "photo_sharing" "health_nutrition"
 [2,] "school"          "college_uni"     "art"             "chatter"       "personal_fitness"
 [3,] "fashion"         "sports_playing"  "music"           "shopping"      "food"            
 [4,] "chatter"         "art"             "small_business"  "politics"      "religion"        
 [5,] "uncategorized"   "spam"            "uncategorized"   "automotive"    "parenting"       
 [6,] "beauty"          "family"          "current_events"  "news"          "outdoors"        
 [7,] "home_and_garden" "small_business"  "college_uni"     "computers"     "sports_fandom"   
 [8,] "business"        "adult"           "crafts"          "travel"        "school"          
 [9,] "small_business"  "home_and_garden" "home_and_garden" "fashion"       "family"          
[10,] "crafts"          "tv_film"         "business"        "cooking"       "eco"    


From this summary, we can 
      | 1                 | 2                 | 3                 | 4               | 5                
----- | ----------------- | ----------------- | ----------------  | --------------- | --------  
 [1,] |"dating"           | "online gaming"   | "tv film"         | "photo sharing" | "health nutrition"
 [2,] |"school"           | "college uni"     | "art"             | "chatter"       | "personal_fitness"
 [3,] |"fashion"         "sports playing"  "music"           "shopping"      "food"            
 [4,] |"chatter"         "art"             "small business"  "politics"      "religion"        
 [5,] | "uncategorized"   "spam"            "uncategorized"   "automotive"    "parenting"       
 [6,] | "beauty"          "family"          "current events"  "news"          "outdoors"        
 [7,] "home and garden" "small business"  "college uni"     "computers"     "sports_fandom"   
 [8,] "business"        "adult"           "crafts"          "travel"        "school"          
 [9,] "small business"  "home and garden" "home and garden" "fashion"       "family"          
[10,] "crafts"          "tv film"         "business"        "cooking"       "eco"    


From this summary, we can 

